---
title: "Github Conflict Demo"
author: "Viva"
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: yes
    theme: flatly
    toc_float: yes
    code_folding: hide
    number_sections: no
  pdf_document:
    toc: yes
---

## Setup 
First let's set up our chunk options and required libraries. This will minimize clutter and remove unnecessary messages and warnings. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE
)

library(tidyverse)
library(ggplot2)
library(sf)
library(mapview)

```

## Load data
Next we load our dataset from OpenDataPhilly.org. This dataset is a GeoJSON of all the parks in Philadelphia. We use sf::st_read() to read in spatial data like this.
```{r load data, include = FALSE}
parks <- st_read("https://opendata.arcgis.com/datasets/d52445160ab14380a673e5849203eb64_0.geojson")
```

## Preview data
Let's preview our data. Using mapview::mapview(), we can quickly check what the data looks like. 
```{r preview data}
#<<<<<<< HEAD
#mapview(parks, col.regions = "white", map.types = "CartoDB.DarkMatter")
#=======
mapview(parks, col.regions = "red", map.types = "CartoDB.DarkMatter")
#>>>>>>> 31aa5eff3ca0c95c7fbb05a5fce08214d753ce5e
```
## Map the data
Finally, let's map using ggplot2. Add your name as a subtitle in the labs() function. Also feel free to change the colors and other aesthetics. Once you're satisfied, save and commit. 
```{r map data}
ggplot() +
  geom_sf(data = parks, fill = "chartreuse4", color = "transparent") +
  labs(title = "Philadelphia Park System, 2023") + 
  theme_void()
```
